Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-05 thesis/paper.tex
blabla
Re-updated event

%%Relate it to Categories
%%What she said
The addition of axserialport was requested by API users. A possible use case, which was given during the interview involved a ticketing system which allows for joint analysis of data from both devices. As such it was included in version 2.0, to meet the demand of the API users.

@@

%%What she said 
%%Re-write this... the main reason was functioanlity and not usability stuff XXX
The interviewee outlined that the previous version of axevent, event, was deprecated in favour. The primary reason for this was to bring the implementation into line with the new design of the event system and interfaces. The interviewee expressed that they were unsatisfied with certain usability aspects of the API.

The interviewee outline that the previous version of axevent, event, was deprecated in favour of a redesigned event system. This redesign was also a good opportunity to implement the new interface design.

%%Category based on her information
Groomative is therefore the obvious choice for the main category for this change with enhancive being the subcategory. This is the reverse of what we concluded and as such means that we incorrectly determined the intent for this change.

From the discussion in the interview, it clear that both of our categorisations were correct; this change was primarily enhancive and secondarily groomative.

@@

This change is very similar to the previously mentioned change and as such is classified in the same way; a main categorisation of enhancive with groomative as the subcategory of change.

The main driving force for this change was the re-implementation and addition of functionality to the axhttp module. Redesigning the module to take advantage of the design was an added bonus.

Our categorisation of enhancive and groomative was therefore correct for this change. The primary intent was to add functionality while also allowing the re-implementation accommodate the new design.

>>>>

%%What she said
The addition of axserialport was requested by API users. A possible use case, which was given during the interview involved a ticketing system which allows for joint analysis of data from both devices. As such it was included in version 2.0, to meet the demand of the API users.

@@

%%What she said 
The interviewee outlined that the previous version of axevent, event, was deprecated in favour of a re-implemention of the new event system. The interviewee expressed that they were unsatisfied with certain usability aspects of the API. event was then completely re-implemented and as a secondary concern, adopted the new system design being used in version 2.0

%%Category based on her information
From the discussion in the interview, it clear that both of our categorisations were correct; this change was primarily enhancive and secondarily groomative.

@@

%%Relate it to Categories
This change is very similar to the previously mentioned change and as such is classified in the same way; a main categorisation of enhancive with groomative as the subcategory of change.

%%What she said 
The main driving force for this change was the re-implementation and addition of functionality to the axhttp module. Redesigning the module to take advantage of the design was an added bonus.

%%Category based on her information
Our categorisation of enhancive and groomative was therefore correct for this change. The primary intent was to add functionality while also allowing the re-implementation accommodate the new design.
